### 2013-02-15 doc/icml2013/evaluation.tex
Added some figures and a table

\subsection{Setup}

@@

We ran expectation-maximization until the log likelihood converged
$10^-5$. Initialized the entries of $\beta$ with a random Gaussian, $\normal{0}{1}$.

In all our experiments, EM converged.

Describe spectral (briefly pointing to algorithm);
initialization, clipping.

Describe spectral+EM

\paragraph{Datasets}
Describe the Curves dataset.
$x = (1, t, t^4, t^9)$
$d = b^p$

Distribution over $x$.

Canonical settings:

Default values:
$n = 10^5$
$k = 5$

Dataset 1: visualization ($b = 1, p = 3$) 
Plot for visualization

Table on different settings: 
  (To show that we work comparably or better to EM always)
  (Spawned!)

Dataset 2: $b = 30$, $p = 1$
(Spawned many tasks to find spec performance. Will run EM on interesting cases)

@@

@@

Curves dataset 2.
Plot: $n$ versus error for various algorithms

@@

\paragraph{Effect of dimensionality}

>>>>

\todo{Fill it up with juicy bits once we actually have them graphs.}

\subsection{Experimental Setup}

@@

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent algorithm\citationneeded. The
algorithm was initialized with the regularized least squares solution
and was run to convergence in each instance. Both regularization
parameters were annealed as $\frac{1}{T}$.

As a baseline, we also implemented EM with two different
initializations. For the first, we used $\beta$s with random standard
Gaussian entries and uniform mixture probabilities, $\pi$. In the other,
we initialized EM with the starting points given by Spectral Experts.

\paragraph{Datasets}

We generated synthetic data using covariates from the unit hyper cube
and non-linear responses.  To conform to the identifiability criteria
discussed in \sectionref{sec:algo}, we considered only features that
would guarantee this condition.

As an example, one set of features we considered in the uni-dimensional
setting were $\{1, x, x^4, x^7\}$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using spectral experts are shown in
\figureref{fig:curves}.

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
    \hspace{-2em}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

%Default values:
%$n = 10^6$
%$k = 5$

\begin{table*}[t]
\caption{Parameter Recovery ($N = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

  \begin{tabular}{ >{\centering}p{5cm}<{\centering} r c c c }
\hline
\abovespace\belowspace
Features  & $K$ & Spectral & EM & Spectral + EM \\
\hline
\abovespace
$\{1$, $ x_1$, $ x_1^4\}$ 
  & 2 & 2.54 $\pm$ 2.81 & 0.28 $\pm$ 0.82 & 0.13 $\pm$ 0.55 \\
$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  & 3 & 3.93 $\pm$ 5.82 & 0.33 $\pm$ 0.96 & 0.35 $\pm$ 1.23 \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  & 5 & 5.27 $\pm$ 2.32 & 1.80 $\pm$ 1.80 & 1.51 $\pm$ 1.77 \\
$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2$, $ x_1^3 x_2^4$, $ x_1^4 x_2^3 \}$ 
  & 7 & 8.42 $\pm$ 1.66 & 7.41 $\pm$ 2.99 & 7.31 $\pm$ 2.47 \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
  & 3 & 3.78 $\pm$ 0.90 & 0.67 $\pm$ 1.49 & 0.51 $\pm$ 1.12 \\
$\{1$, $ x_1$, $ x_2$, $ x_3$, $ x_1 x_2 x_3^2$, $ x_1 x_2^2 x_3$, $ x_1^2 x_2 x_3$, $ x_1^2 x_2^2$, $ x_1^2 x_3^2$, $ x_2^2 x_3^2$, $ x_3^2\}$
  & 7 & 9.97 $\pm$ 3.22 & 1.43 $\pm$ 1.97 & 1.42 $\pm$ 2.17 \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table*}

\todo{Dataset 2}: $b = 30$, $p = 1$ [TODO]

@@

\paragraph{Misspecified Data}

To show how well spectral methods can handle mis-specification, we
compared the performance of the different algorithms with entire
segments removed from the generated data. \todo{Table X shows figures}.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{figures/vs-n/1-8-3-3.pdf}
  \caption{}
  \label{fig:vs-n}
\end{figure}

\todo{We see that the error of spectral is actually less than EM after a point.}

@@
